Merging Datasets Through Deep learning

### 2018-09-04 paper2018/relatedWork.tex
global loss wording

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.  Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard negative triplet mining \cite{songCVPR17} using an indirect mechanism to do so.  Our approach directly mines hard negative triplets, so there is no need to try to broaden the loss function to a batch.

>>>>

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.   Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.
